Total Score

### 2023-02-06 src/MSAtotal_scores.Rmd
rename legend names

ggplot(data = score_tidy, aes(y = reorder(cbsa, FINAL_owen_SCORE), x = criteria_score, fill = criteria_labels)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
scale_fill_discrete(labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord")) +
   scale_fill_manual(values = c("#FDB462", "gold", "palevioletred1",  "#BC80BD", "#6699CC", "#44AA99"))

>>>>

ggplot(data = score_tidy, aes(y = reorder(cbsa, FINAL_owen_SCORE), x = criteria_score)) + 
    geom_col(aes(fill = criteria)) +
  labs(x = "Total Score (Client)",
       y = " ") +
  guides(fill=guide_legend(title="Criteria (weighted)")) +
   scale_fill_manual(values = c("#FDB462", "gold", "palevioletred1",  "#BC80BD", "#6699CC", "#44AA99"),
                     labels=c('Climate Risk', 'CO2 Emissions', 'Electricity', "Finances", "Real Estate", "Landlord")) +
  scale_y_discrete((labels = score_tidy$city_msa))
